```{r}
library(dplyr)
library(lubridate)
library(stringr)
library(tidyr)
library(labelled)
library(survey)
library(caret)
library(cvms)
library(tibble)
library(pROC)
library(DescTools)
library(sjPlot)
set.seed(1)

```

---
After making the data usable, a binary regression will be used to explain green voting behaviour based on certain voter characteristics.
We want to explain is_green (so if the given respondent voted for a green party). The items of the logistic regression were chosen according to the generally mentioned factors in literature.

X003: age - numeric
X025A_01: education - factor
F034: religion - factor
Y002: post-materialism - factor
E033: self-positioning - numeric
E027: attending protests - factor
---

```{r}
raw.EVS$X025A_01 <- as.factor(raw.EVS$X025A_01)
raw.EVS$F034 <- as.factor(raw.EVS$F034)
raw.EVS$Y002 <- as.factor(raw.EVS$Y002)
raw.EVS$E027 <- as.factor(raw.EVS$E027)

hist(raw.EVS$X003)
hist(raw.EVS$E033)

logit_model <- glm(is_green ~ X003 + X025A_01 + F034 + Y002 + E033 + E027, data = raw.EVS)
s <- summary(logit_model)

```

Model evaluation

```{r}
raw.EVS$Predicted <- predict(logit_model, raw.EVS, type='response')

class_matrix <- table(raw.EVS[,c("is_green", "Predicted")])
ROC_data <- roc(raw.EVS$is_green, raw.EVS$Predicted)
summary(ROC_data)
plot(ROC_data)



regTermTest(logit_model, "F034")
regTermTest(logit_model, "X003")
regTermTest(logit_model, "X025A_01")
regTermTest(logit_model, "F034")
```

```{r}
hist(raw.EVS$X003)
esquisse::esquisser()
```
COR
```{r}
na.omit(raw.EVS)
corr <-  cor(raw.EVS[, c('X003','X025A_01','F034','Y002', 'E033', 'E027')], method = 'pearson')
corrplot(corr, method = 'color', insig="p-value", addCoef.col = "black", sig.level = 0.05)

raw.EVS <- raw.EVS[!is.na(raw.EVS$E027), -1]
df.b <- df[!is.na(df$B), -2]
```
CONFUSION MATRIX
```{r}

```

